\section*{Future Technological Trends}
It is projected that the swarm robotics market to reach about 35.79 billion USD by 2030 with a compound annual growth rate (CAGR) of 17.20 percent, from the 2022 market value of 7.91 billion USD, which indicates a potential 400 percent increase in value within the next decade [60-62]. This can imply that the advancements in technological infrastructure for swarming will begin to populate markets across industries and will promote versatile applications for the tactic. Swarming is currently being integrated into several enterprises, such as space exploration, agriculture, medicine, and even computing []. For example, recent study conducted by NASA [63] assessed the applicability of swarm technology in exploring astral terrain. Swarm intelligence in autonomous units present the potential to dramatically improve our ability to efficiently locate, identify and collect resources over large and previously explored territory.

\section*{Conclude}
Swarm technology intelligently combines multi-agent coordination and collaboration to accomplish an objective and can offer more added value to strategy when compared to massive attacks.  To define a swarm, we must assess all the features within the entity and prescribe a comprehensive evaluation of each. We must properly assess the functionality, technological capabilities, and overall behavior to effectively control and combat swarm-based threat scenarios. Although existing infrastructure to support intelligent swarming is in its infancies, there remains the potential for the development of such sophisticated cyber-physical systems. It can be inferred that current countermeasures are not designed to specifically counter swarm technology, which concludes that countermeasures must continue to evolve along with the technology to effectively protect against the use of these entities. A proper definition of swarming will propel the technological front outside the defense sector, and swarms will have found their way into space, agriculture, maritime, and consumer technology.